% Profile / Header

\begin{center}
    {\Large \textbf{\FullName}}\\
    \Location \\[6pt]

    Phone: \Phone \quad
    Email: \href{mailto:\Email}{\Email} \\

    LinkedIn: \href{\LinkedInURL}{\LinkedInText} \quad
    GitHub: \href{\GitHubURL}{\GitHubText} \\

    Instagram: \href{\InstagramURL}{\InstagramText} \quad
    Website: \href{\WebsiteURL}{\WebsiteText}
\end{center}

\vspace{8pt}

\cvsection{\ifenglish Profile\else Profil\fi}

\ifenglish
I am Reza Chairul Manam, a graduate in Informatics Engineering from Institut Teknologi Sumatera with a focus as a Full-Stack Developer, particularly in web and WebGIS development. I have experience building web applications using Laravel, React, PostgreSQL, and Tailwind CSS, with a strong interest in geospatial data processing and visualization. In addition to technical skills, I am proficient in Microsoft Office for documentation and analysis purposes. I possess strong communication and leadership skills, both in individual work and team collaboration, and I am accustomed to working in a structured, adaptable, and problem-solving-oriented environment.
\else
Saya Reza Chairul Manam, lulusan Teknik Informatika dari Institut Teknologi Sumatera dengan fokus sebagai Full-Stack Developer, khususnya dalam pengembangan web dan WebGIS. Saya berpengalaman membangun aplikasi web menggunakan Laravel, React, PostgreSQL, dan Tailwind CSS, serta memiliki ketertarikan kuat pada pengolahan dan visualisasi data geospasial. Selain kemampuan teknis, saya menguasai Microsoft Office untuk kebutuhan dokumentasi dan analisis. Saya memiliki kemampuan komunikasi dan kepemimpinan yang baik, baik dalam kerja individu maupun kolaborasi tim, serta terbiasa bekerja secara terstruktur, adaptif, dan berorientasi pada penyelesaian masalah.
\fi