% Projects

\cvsection{\ifenglish Projects\else Proyek\fi}

% =========================
% 2023
% =========================
\textbf{\ifenglish Village Information System Implementation (OpenSID)\else Implementasi Sistem Informasi Desa (OpenSID)\fi} \hfill \textbf{2023} \\
\ifenglish Role: System Administrator / Data Operator
\else Peran: Administrator Sistem / Operator Data
\fi
\begin{itemize}[leftmargin=*, itemsep=1pt, topsep=1pt]
\ifenglish
\item Implemented and managed OpenSID-based village information systems while organizing administrative and demographic data to improve digital public services for three villages in South Lampung.
\else
\item Mengimplementasikan dan mengelola sistem informasi desa berbasis OpenSID serta menata data administrasi dan kependudukan untuk meningkatkan layanan digital pada tiga desa di Kabupaten Lampung Selatan.
\fi
\end{itemize}

% =========================
% 2024
% =========================
\textbf{\ifenglish SDGs Center ITERA Website\else Website SDGs Center ITERA\fi} \hfill \textbf{2024} \\
\ifenglish Role: Front-End Developer
\else Peran: Front-End Developer
\fi
\begin{itemize}[leftmargin=*, itemsep=1pt, topsep=1pt]
\ifenglish
\item Developed responsive front-end components using Laravel and collaborated with backend developers to improve usability and maintainability of the SDGs Center ITERA website.
\else
\item Mengembangkan komponen front-end responsif menggunakan Laravel serta berkolaborasi dengan backend developer untuk meningkatkan kegunaan dan keberlanjutan pengembangan website SDGs Center ITERA.
\fi
\end{itemize}

% =========================
% 2023–2025
% =========================
\textbf{\ifenglish PLN NP UPDK Inventory Management System (K3 Division)\else Sistem Manajemen Inventaris PLN NP UPDK (Divisi K3)\fi} \hfill \textbf{2023--2025} \\
\ifenglish Role: Full-Stack Developer (Internship)
\else Peran: Full-Stack Developer (Magang)
\fi
\begin{itemize}[leftmargin=*, itemsep=1pt, topsep=1pt]
\ifenglish
\item Designed and developed a web-based inventory monitoring system for the K3 division of PLN NP UPDK Bandar Lampung to digitize equipment tracking and improve efficiency in inventory management.
\else
\item Merancang dan mengembangkan sistem monitoring inventaris berbasis web untuk Divisi K3 PLN NP UPDK Bandar Lampung guna mendigitalisasi pelacakan peralatan dan meningkatkan efisiensi pengelolaan inventaris.
\fi
\end{itemize}

% =========================
% 2025
% =========================
\textbf{\ifenglish Star Warship Arcade Game\else Game Arcade Star Warship\fi} \hfill \textbf{2025} \\
\ifenglish Role: Project Manager \& Developer
\else Peran: Project Manager \& Developer
\fi
\begin{itemize}[leftmargin=*, itemsep=1pt, topsep=1pt]
\ifenglish
\item Led development of a simple arcade game project while coordinating a small development team and implementing core gameplay mechanics.
\else
\item Memimpin pengembangan proyek game arcade sederhana sekaligus mengoordinasikan tim kecil pengembang dan mengimplementasikan mekanisme gameplay utama.
\fi
\end{itemize}

% =========================
% 2026
% =========================
\textbf{\ifenglish UKMBSM ITERA Web Profile (Ongoing)\else Web Profile UKMBSM ITERA (Berjalan)\fi} \hfill \textbf{2026} \\
\ifenglish Role: Full-Stack Developer
\else Peran: Full-Stack Developer
\fi
\begin{itemize}[leftmargin=*, itemsep=1pt, topsep=1pt]
\ifenglish
\item Developing a full-stack organizational website to improve information accessibility and strengthen the digital presence of UKMBSM ITERA.
\else
\item Mengembangkan website organisasi berbasis full-stack untuk meningkatkan aksesibilitas informasi dan memperkuat kehadiran digital UKMBSM ITERA.
\fi
\end{itemize}